Impact of IPTp Regimen on Pregnancy Outcomes in a Malaria-Endemic Setting

### 2025-04-26 products/manuscript/Manuscript.qmd
update6

dding an interaction term between total malaria episodes and SP (reference = DP) significantly improved model fit (ΔDeviance = 10.11 on 1 df; p = 0.0015). The interaction coefficient (SP × episodes) was highly significant (OR 1.47; 95% CI 1.16–1.88; p = 0.002), indicating that each additional malaria episode increases the odds of an adverse outcome by 47% more under SP than under DP. In practical terms, at zero episodes, the predicted probability of an adverse outcome is similar for both arms (~ 0.55) but diverges sharply by three episodes: ~ 0.62 for DP versus ~ 0.78 for SP (Figure 2). Full model estimates are given in Table 4.

@@

#  Remove Section

*Include citations in your Rmd file using bibtex, the list of references will automatically be placed at the end*

This paper [@leek2015] discusses types of analyses.

These papers [@mckay2020; @mckay2020a] are good examples of papers published using a fully reproducible setup similar to the one shown in this template.

Note that this cited reference will show up at the end of the document, the reference formatting is determined by the CSL file specified in the YAML header. Many more style files for almost any journal [are available](https://www.zotero.org/styles). You also specify the location of your bibtex reference file in the YAML. You can call your reference file anything you like.

>>>>

Adding an interaction term between total malaria episodes and SP (reference = DP) significantly improved model fit (ΔDeviance = 10.11 on 1 df; p = 0.0015). The interaction coefficient (SP × episodes) was highly significant (OR 1.47; 95% CI 1.16–1.88; p = 0.002), indicating that each additional malaria episode increases the odds of an adverse outcome by 47% more under SP than under DP. In practical terms, at zero episodes, the predicted probability of an adverse outcome is similar for both arms (~ 0.55) but diverges sharply by three episodes: ~ 0.62 for DP versus ~ 0.78 for SP (Figure 2). Full model estimates are given in Table 4.

@@
